R Notebook

### 2024-02-07 Scripts/data_cleaning.Rmd
Updates to appendix--removing MM

Cleaning nelda variables--this will have to be done for all used variables
```{r}
nelda <- nelda %>% dplyr::rename(first.mp.election = nelda2)
nelda <- nelda %>% rename(protests = nelda9)
nelda <- nelda %>% rename(inc.fav.cancel = nelda34)
nelda <- nelda %>% rename(inc.lose = nelda24)
nelda <- nelda %>% rename(inc.termlimit = nelda8)
nelda <- nelda %>% rename(econ.crisis.nelda = nelda18)
nelda <- nelda %>% rename(opp.votegain = nelda7)
nelda <- nelda %>% rename(nelda.protests.fraud = nelda30)
nelda <- nelda %>% rename(new.elections.held = nelda37)
nelda <- nelda %>% rename(inc.replaced.prot = nelda41)
nelda <- nelda %>% rename(preelection_concerns = nelda11)
nelda <- nelda %>% rename(harass_opp = nelda15)
nelda <- nelda %>% rename(opp_leaders_prevented = nelda13)
nelda <- nelda %>% rename(unscheduled_election = nelda6)
nelda <- nelda %>% rename(inc.run = nelda21)
nelda <- nelda %>% rename(chosen.successor = nelda22)

@@

nelda <- nelda %>% mutate(econ.crisis.nelda = ifelse(econ.crisis.nelda == "yes", 1, ifelse(econ.crisis.nelda == "no", 0, NA)))
nelda <- nelda %>% mutate(opp.votegain = ifelse(opp.votegain == "yes", 1, ifelse(opp.votegain == "no", 0, NA)))
nelda <- nelda %>% mutate(nelda.protests.fraud = ifelse(protests == 0, 0, ifelse(nelda.protests.fraud == "yes", 1, ifelse(nelda.protests.fraud == "no", 0, NA))))
nelda <- nelda %>% mutate(inc.replaced.prot = ifelse(inc.replaced.prot == "yes", 1, 0))
nelda <- nelda %>% mutate(new.elections.held = ifelse(new.elections.held == "yes", 1, 0))

@@

@@

egaldem.1lag ,
altinf.1lag,
api.1lag,
mpi.1lag,
frassoc.1lag,
suffr.1lag,
frefair.1lag,
elecoff.1lag,
liberal.1lag,
partip.1lag,
cspart.1lag,
eqdr.1lag,
oppaut.1lag,
jureform.1lag,
jupurge.1lag,
jupoatck.1lag,
jupack.1lag,
juaccnt.1lag,
juhcind.1lag,
juncind.1lag,
mecenefm.1lag,
gdppcln.1lag,
gdpgro.1lag,
inflat.1lag,
v2elvotbuy,
v2elirreg,
v2elintim, v2elfrfair,
physinteg.1lag, v2x_clphy,
polyarchy_no_ei,
liberal_no_jucon, v2elaccept,
v2cademmob, #pro-democracy mass mob
v2caautmob, #pro-autoc mass mob
v2cagenmob, #scale of mobilization
v2caconmob, #concentration of mobilization in the capital
v2x_regime,
prodem.protest.1lead,
proauth.protest.1lead,
protest.scale.1lead,
concen.protest.1lead,
country_id_year), by = "country_id_year")

@@

@@

## Ideas for adding rate of growth and rate of decay to be used as DVs

 - Quick growth after fraud indicates opp believes state is weak
 - Slow or no growth after fraud indicates opp believes state is strong
 - Quick decay after peak indicates state is strong / believed strong (or not--regime is weak and so quickly collapses)
 - Slow decay after peak indicates state is weak / believed weak

The idea here would be:
  - Replace categorical measures with minimum number (average won't work because top category is top-less)
  - Replace -99 with...
  - Filter by election
  - Group by date and sum
  - Fit exponential function regression to find coefficient for 'r' (rate of growth)
  - This becomes the DV for a regression on fraud

Instead, because protests don't always follow the exponential distribution, going to create a simple measure of protest growth / decay intensity.

The idea here would be:
  - Replace categorical measures with minimum number (average won't work because top category is top-less)
  - Replace -99 with...
  - Filter by election
  - Group by date and sum
  - Find date of largest protest
  - Calculate max_size / max_date - 0 and max_size / end_date - max_date
  - Merge these values into main dataset by election (NeldaID for example)
  - This becomes the DV for a regression on fraud

```{r}
# Example

## Remove things other than protests
ecav_prot <- ecav %>% filter(str_detect(EventName, "rotest") == T | str_detect(EventName, "ccupation") == T |
                                  str_detect(EventName, "lockade") == T) #Only captures protests
```

Replacing NA protest size with average for that wave
```{r}
## Set up holding df

dv_df <- data.frame(NeldaID = NA, avg_size = NA)

## Filter by election and replace -99 with NA for protest size

 election_ids <- unique(ecav_prot$NeldaID)
ecav_prot <- ecav_prot %>% mutate(ParticipantNumber = ifelse(ParticipantNumber == -99, NA, ParticipantNumber))

for(i in 1:length(election_ids)){ 
  ecav_temp <- ecav_prot %>% filter(NeldaID == election_ids[i])  #There is a loop here

    ## Remove protests before election
  ecav_temp <- ecav_temp %>% filter(Date >= Electiondate)
  if(nrow(ecav_temp) == 0){
     new_row <- data.frame(NeldaID = election_ids[i], 
                           avg_size = 0) #No post-election protest

  dv_df[i,] <- new_row
  print(paste0("No post-election protest for observation ", i, "."))
  next
  } else{

  new_row <- data.frame(NeldaID = election_ids[i], avg_size = floor(mean(ecav_temp$ParticipantNumber, na.rm = T)))

  dv_df[i,] <- new_row
  print(paste0("Average size for observation ", i, " completed."))
  }
}

## Merge dv_df back into main dataset

ecav_prot <- ecav_prot %>% left_join(dv_df, by = "NeldaID")

Current to-do: Double-check the output of the size code

```{r}
## Set up holding df

dv_df <- data.frame(NeldaID = NA, prot_intensity = NA, decay_intensity = NA, max_size = NA, day_max = NA)

ecav_prot <- ecav_prot %>% mutate(ParticipantNumber_adj = ifelse(is.na(ParticipantNumber)==T, avg_size, ParticipantNumber))
ecav_prot <- ecav_prot %>% mutate(ParticipantNumber_adj = ifelse(ParticipantNumber_adj == "NaN", 2, ParticipantNumber_adj)) #Assume NA size defaults to category 2

#ecav_rus <- ecav %>% filter(country == "Russia")   # Filter by country
ecav_prot <- ecav_prot %>% mutate(ParticipantNumber_num_min = ifelse(ParticipantNumber_adj == 1, 5, 
                                ifelse(ParticipantNumber_adj == 2, 55, 
                                       ifelse(ParticipantNumber_adj == 3, 550, 
                                              ifelse(ParticipantNumber_adj == 4, 5500,
                                                     ifelse(ParticipantNumber_adj == 5, 10000, NA))))))

## Filter by election

 election_ids <- unique(ecav_prot$NeldaID)

for(i in 1:length(election_ids)){ 
  ecav_temp <- ecav_prot %>% filter(NeldaID == election_ids[i])  #There is a loop here

## Group by date and sum number of participants by date:

 ecav_temp_comb <- ecav_temp %>% mutate(date_col = date(Date)) %>%
    group_by(date_col) %>%
     summarize(total = sum(ParticipantNumber_num_min))

 ## Get eleection date

 election_date_temp <- unique(ecav_temp$Electiondate)

 ## Remove protests before election

 ecav_temp_comb <- ecav_temp_comb %>% filter(date_col >= election_date_temp)

  if (nrow(ecav_temp_comb) == 0) {
    new_row <- data.frame(election_ids[i], NA, NA, NA, NA)
    dv_df[i,] <- new_row
    print(paste0("No post-election protests for obseveration ", i, ", election ID", election_ids[i], ","))
    next}  #End loop if zero post-election protests

 ## Get date of largest protest

 max_data <-  ecav_temp_comb %>% filter(total == max(total, na.rm = T))

  # Assign NA to NA size
 if (nrow(max_data)==0){
    new_row <- data.frame(election_ids[i], NA, NA, NA, NA)
    dv_df[i,] <- new_row
    print(paste0("Election observation ", i, " completed. (Note: no size estimate."))
    next
 }

  if (nrow(max_data) >= 1) {
    prot_intensity <- max_data$total[1] / (1 + as.numeric(ymd(max_data$date_col[1]) - ymd(election_date_temp))) #[1] gets the first peak
    last_peak <- tail(max_data, n = 1)
    decay_intensity <-  last_peak$total / (1 + as.numeric(max(ecav_temp_comb$date_col) - (ymd(last_peak$date_col))))
    day_max <- as.numeric(ymd(max_data$date_col[1]) - ymd(election_date_temp))
    new_row <- data.frame(election_ids[i], prot_intensity, decay_intensity, max_data$total[1], day_max)
  new_row <- new_row %>% rename(max_size = max_data.total.1.)
    dv_df[i,] <- new_row
    print(paste0("Election observation ", i, " completed. (Note: multiple peaks."))
    next
  }

 ## Calculate DVs

 prot_intensity <- max_data$total / (1 + as.numeric(ymd(max_data$date_col) - ymd(election_date_temp)))
 decay_intensity <-  max_data$total / (1 + as.numeric(max(ecav_temp_comb$date_col) - (ymd(max_data$date_col)))) #The +1 is a kludge to prevent Inf values

 ##Add to holding df

  day_max <- as.numeric(ymd(max_data$date_col[1])) - as.numeric(ymd(election_date_temp))
  new_row <- data.frame(election_ids[i], prot_intensity, decay_intensity, max_data$total, day_max)
  new_row <- new_row %>% rename(max_size = max_data.total)

  dv_df[i,] <- new_row
  print(paste0("Election observation ", i, " completed."))

  ## Merge dv_df back into main dataset

nelda2.sub.b <- nelda2.sub %>% left_join( dv_df, by = "NeldaID")

```  
Pick up here with fixing this code:

```{r, eval=FALSE}
dv_df <- data.frame(NeldaID = NA, growth_coef = NA)
for(i in 1:length(election_ids)){
 ecav_temp <- ecav_prot %>% filter(NeldaID == election_ids[i])  #There is a loop here

###Getting a regression slope for protest size and time
  ecav_temp_comb <- ecav_temp %>% mutate(date_col = date(Date)) %>%
    group_by(date_col) %>%
     summarize(total = sum(ParticipantNumber_num_min))
  max_date_reg <- ecav_temp_comb %>% filter(total == max(total)) %>%  
   dplyr::select(date_col)

 ecav_temp_reg <- ecav_temp %>% filter(as_date(Date) >= as_date(Electiondate))
 ecav_temp_reg <- ecav_temp_reg %>% mutate(date_col = date(Date))
 ecav_temp_reg <- ecav_temp_reg %>% left_join(ecav_temp_comb, by = "date_col")  #Gets totals by date

 ecav_temp_reg <- ecav_temp_reg %>% filter(as_date(Date) <= max_date_reg[1,1])
 ecav_temp_reg <- ecav_temp_reg %>% mutate(date_index = as.numeric(ymd(ecav_temp_reg$Date) - ymd(Electiondate)))
 if(nrow(ecav_temp_reg) == 0) {
   new_row <- data.frame(election_ids[i], NA)
   dv_df[i,] <- new_row
   print(paste0("No observations for election number ", i, "."))
   next
 }
 if(length(unique(ecav_temp_reg$Date))==1){
   growth_coef <-  ((ecav_temp_reg$total - 0 )/((ecav_temp_reg$date_index+1)-0))[1] #m = (y2 - y1)/(x2 - x1) #+1 in denominator is a kludge to avoid Inf values for day 0 protests
   new_row <- data.frame(election_ids[i], growth_coef)
   dv_df[i,] <- new_row
   print(paste0("One date observed for election ", i, "."))
   next
 } else {

 fit <- lm(total ~ 0 + date_index, ecav_temp_reg)
 sum_table <- summary(fit)
 growth_coef <- sum_table$coefficients[1]
  new_row <- data.frame(election_ids[i], growth_coef)
   dv_df[i,] <- new_row
   print(paste0("Coefficient estimated for election ", i, "."))
 }
 rm(growth_coef)
}

## Merge dv_df back into main dataset

nelda2.sub.b <- nelda2.sub.b %>% left_join( dv_df, by = "NeldaID")
```

@@

```{r}
success_cases <- nelda2.sub.b %>% filter(inc.replaced.prot == 1 | nelda35 == "yes") %>% dplyr::select(e_regionpol, year, election_mdy)

@@

nelda2.sub.b <- nelda2.sub.b %>% mutate(regional_success_lag = ifelse(e_regionpol == 1 & (election_mdy %within% interval(start = "1990-06-17", end = "1991-06-17") | election_mdy %within% interval(start = "2000-09-24", end = "2001-09-24") | election_mdy %within% interval(start = "2003-11-02", end = "2006-11-06")), 1, 
                                      ifelse(e_regionpol == 4 & (election_mdy %within% interval(start = "1997-04-13", end = "1998-04-13") | election_mdy %within% interval(start = "1998-05-23", end = "1999-05-23") | election_mdy %within% interval(start = "2000-10-22", end = "2001-10-22") | election_mdy %within% interval(start = "2007-07-22", end = "2008-07-22") | election_mdy %within% interval(start = "2010-11-28", end = "2011-11-28")), 1, 
                                             ifelse(e_regionpol == 2 & (election_mdy %within% interval(start = "2000-04-09", end = "2001-04-09") | election_mdy %within% interval(start = "2000-05-28", end = "2001-05-28") | election_mdy %within% interval(start = "2006-02-07", end = "2007-02-07")), 1, 
                                                    ifelse(e_regionpol == 8 & (election_mdy %within% interval(start = "1989-11-22", end = "1990-11-22")  | election_mdy %within% interval(start = "1996-02-15", end = "1997-02-15")), 1, 0)))))
```

```{r}
write.csv(nelda2.sub.b, here::here("Data", "nelda2_sub_2023-05-30.csv"))
```

@@

```{r, eval=FALSE}
nelda2.sub <- read.csv(here::here("Data", "nelda2_sub_2023-05-10.csv"))
ert <- read.csv(here::here("Data", "ert.csv"))
ert <- ert %>% filter(year > 1988)
ert.sub <- ert %>% dplyr::select(year, country_id, country_name, reg_start_year)
ert.sub <- ert.sub %>% mutate(country_id_year = paste(country_id, year, sep = "_"))

@@

nelda2.sub  <- nelda2.sub %>% mutate(regime_age = year - reg_start_year)

write.csv(nelda2.sub, here::here("Data", "nelda2_sub_2023-05-30.csv"))

@@

>>>>

Cleaning nelda variables--this will have to be done for all used variables
```{r}
nelda <- nelda %>% dplyr::rename(first.mp.election = nelda2)
nelda <- nelda %>% rename(protests = nelda29)
nelda <- nelda %>% rename(protest.fraud.allege = nelda30)
nelda <- nelda %>% rename(inc.fav.cancel = nelda34)
nelda <- nelda %>% rename(inc.lose = nelda24)
nelda <- nelda %>% rename(inc.termlimit = nelda8)
nelda <- nelda %>% rename(econ.crisis.nelda = nelda18)
nelda <- nelda %>% rename(inc.confident = nelda12)
nelda <- nelda %>% rename(opp.votegain = nelda27)
nelda <- nelda %>% rename(new.elections.held = nelda37)
nelda <- nelda %>% rename(inc.replaced.prot = nelda41)
nelda <- nelda %>% rename(preelection_concerns = nelda11)
nelda <- nelda %>% rename(harass_opp = nelda15)
nelda <- nelda %>% rename(opp_leaders_prevented = nelda13)
nelda <- nelda %>% rename(unscheduled_election = nelda6)
nelda <- nelda %>% rename(inc.run = nelda21)
nelda <- nelda %>% rename(chosen.successor = nelda22)

@@

nelda <- nelda %>% mutate(econ.crisis.nelda = ifelse(econ.crisis.nelda == "yes", 1, ifelse(econ.crisis.nelda == "no", 0, NA)))
nelda <- nelda %>% mutate(opp.votegain = ifelse(opp.votegain == "yes", 1, ifelse(opp.votegain == "no", 0, NA)))
nelda <- nelda %>% mutate(protest.fraud.allege = ifelse(protests == 0, 0, ifelse(protest.fraud.allege == "yes", 1, ifelse(protest.fraud.allege == "no", 0, NA))))
nelda <- nelda %>% mutate(inc.replaced.prot = ifelse(inc.replaced.prot == "yes", 1, 0))
nelda <- nelda %>% mutate(new.elections.held = ifelse(new.elections.held == "yes", 1, 0))

@@

vdem.recent <- vdem.recent %>% group_by(country_id) %>% mutate(antisys.1lag = lag(v2csantimv))
vdem.recent <- vdem.recent %>% group_by(country_id) %>% mutate(csenv.1lag = lag(v2csprtcpt))
vdem.recent <- vdem.recent %>% group_by(country_id) %>% mutate(patronage.appts.1lag = lag(v2stcritrecadm))
vdem.recent <- vdem.recent %>% group_by(country_id) %>% mutate(state.owned.1lag = lag(v2clstown))
vdem.recent <- vdem.recent %>% group_by(country_id) %>% mutate(polariz.1lag = lag(v2cacamps))
vdem.recent <- vdem.recent %>% group_by(country_id) %>% mutate(regime.1lag = lag(v2x_regime))
vdem.recent <- vdem.recent %>% group_by(country_id) %>% mutate(wb_inst.1lag = lag(e_wbgi_pve))

@@

                                                  antisys.1lag,
                                                  v2csantimv,
                                                  csenv.1lag,
                                                  v2csprtcpt,
                                                  patronage.appts.1lag,
                                                  v2stcritrecadm,
                                                  state.owned.1lag,
                                                  v2clstown,
                                                  v2elembaut,
                                                  v2cacamps,
                                                  polariz.1lag,
                                                  regime.1lag,
                                                  wb_inst.1lag,

egaldem.1lag ,
altinf.1lag,
api.1lag,
mpi.1lag,
frassoc.1lag,
suffr.1lag,
frefair.1lag,
elecoff.1lag,
liberal.1lag,
jucon.1lag,
partip.1lag,
cspart.1lag,
eqdr.1lag,
oppaut.1lag,
jureform.1lag,
jupurge.1lag,
jupoatck.1lag,
jupack.1lag,
juaccnt.1lag,
juhcind.1lag,
juncind.1lag,
mecenefm.1lag,
gdppcln.1lag,
gdpgro.1lag,
inflat.1lag,
v2elvotbuy,
v2elirreg,
v2elintim, v2elfrfair,
physinteg.1lag, v2x_clphy,
polyarchy_no_ei,
liberal_no_jucon, v2elaccept,
v2cademmob, #pro-democracy mass mob
v2caautmob, #pro-autoc mass mob
v2cagenmob, #scale of mobilization
v2caconmob, #concentration of mobilization in the capital
v2x_regime,
prodem.protest.1lead,
proauth.protest.1lead,
protest.scale.1lead,
concen.protest.1lead,
country_id_year), by = "country_id_year")

@@

##Amended vote-shares 2 followed the following coding rules:
#- Seat shares instead of vote-shares where the latter are not provided
#   -This is true of many post-communist and highly authoritarian countries (i.e. not missing at random)
#- Independents used as largest party when there is no ruling party but parties are allowed
#- Lebanon is excluded due to consociational structure w/ independents mixing with parties
#- Iran is also excluded due to the absence of real parties (though there are factions)

winner.shares2 <- read.csv(here::here("Data", "amended_vote_shares2.csv"))
nelda2.sub <- nelda2.sub %>% left_join(winner.shares2, by = "NeldaID")

nelda2.sub <- nelda2.sub %>% mutate(winner.share.upd = ifelse(types == "Executive", v2elvotlrg_amend/100, v2ellovtlg_amend/100))

nelda2.sub <- nelda2.sub %>% mutate(winner.share.upd = ifelse(is.na(winner.share.upd)==F, winner.share.upd,
                                                ifelse(types == "Executive", v2elvotlrg_amend_2/100, v2ellovtlg_amend_2/100)))

@@

@@

```{r}
success_cases <- nelda2.sub %>% filter(inc.replaced.prot == 1 | nelda35 == "yes") %>% dplyr::select(e_regionpol, year, election_mdy)

@@

nelda2.sub <- nelda2.sub %>% mutate(regional_success_lag = ifelse(e_regionpol == 1 & (election_mdy %within% interval(start = "1990-06-17", end = "1991-06-17") | election_mdy %within% interval(start = "2000-09-24", end = "2001-09-24") | election_mdy %within% interval(start = "2003-11-02", end = "2006-11-06")), 1, 
                                      ifelse(e_regionpol == 4 & (election_mdy %within% interval(start = "1997-04-13", end = "1998-04-13") | election_mdy %within% interval(start = "1998-05-23", end = "1999-05-23") | election_mdy %within% interval(start = "2000-10-22", end = "2001-10-22") | election_mdy %within% interval(start = "2007-07-22", end = "2008-07-22") | election_mdy %within% interval(start = "2010-11-28", end = "2011-11-28")), 1, 
                                             ifelse(e_regionpol == 2 & (election_mdy %within% interval(start = "2000-04-09", end = "2001-04-09") | election_mdy %within% interval(start = "2000-05-28", end = "2001-05-28") | election_mdy %within% interval(start = "2006-02-07", end = "2007-02-07")), 1, 
                                                    ifelse(e_regionpol == 8 & (election_mdy %within% interval(start = "1989-11-22", end = "1990-11-22")  | election_mdy %within% interval(start = "1996-02-15", end = "1997-02-15")), 1, 0)))))
```

@@

```{r, eval=FALSE}
ert <- read.csv(here::here("Data", "ert.csv"))
ert <- ert %>% filter(year > 1988)
ert.sub <- ert %>% dplyr::select(year, country_id, country_name, reg_start_year)
ert.sub <- ert.sub %>% mutate(country_id_year = paste(country_id, year, sep = "_"))

@@

nelda2.sub  <- nelda2.sub %>% mutate(regime_age = year - reg_start_year)
```

## DIEM data for cross-checking export coding in VDEM

```{r}
load(here::here("Data", "diem_data.rda"))
diem <- da31461.0001
rm(da31461.0001)

##Convert diem's COW identifiers to the vdem type used above, variable called country_id

diem <- diem %>% mutate(country_id = countrycode(sourcevar = COW, origin = "cown", destination = "vdem")) #Needs fixes for a couple countries

diem <- diem %>% rename(diem_fraud_max = MAXR211R)
diem <- diem %>% rename(diem_explicheat_max = MAXR21CHEAT)
diem <- diem %>% rename(presidential = EXELEC)
diem <- diem %>% mutate(country_id_year = paste(country_id, YEAR, sep = "_"))

#####Convert variables to numeric

diem <- diem %>% mutate(diem_fraud_max = ifelse(is.na(diem_fraud_max)==T, NA, 
                                                ifelse(diem_fraud_max == "(0) Good - no problems", 0,
                                                       ifelse(diem_fraud_max == "(1) Low - minor problems only", 1, 
                                                              ifelse(diem_fraud_max == "(2) Moderate - moderate problems", 2, 3)))))

diem <- diem %>% mutate(diem_explicheat_max = ifelse(is.na(diem_explicheat_max)==T, NA, 
                                                ifelse(diem_explicheat_max == "(0) Good - no problems", 0,
                                                       ifelse(diem_explicheat_max == "(1) Low - minor problems only", 1, 
                                                              ifelse(diem_explicheat_max == "(2) Moderate - moderate problems", 2, 3)))))

diem <- diem %>% mutate(presidential = ifelse(presidential == "(1) Executive Election", 1, 0))

#####

## Find average of observer reports per election

mean_max_fraud <- diem %>% group_by(NEWID) %>% summarise(mean(diem_fraud_max))
mean_max_explicheat <- diem %>% group_by(NEWID) %>% summarise(mean(diem_explicheat_max))

## Get month and year for each election

diem <- diem %>% mutate(MONTH = ifelse(is.na(DATEEXEC)==T, DATELEG, DATEEXEC))

diem <- diem %>% mutate(country_id_year_month = paste(country_id, YEAR, MONTH, sep = "_"))

## For merging

diem_sub <- diem %>% dplyr::select(country_id_year_month, diem_explicheat_max, diem_fraud_max)
diem_sub <- diem_sub %>%
  distinct(.keep_all = TRUE)

##Get month separately for NELDA

nelda2.sub <- nelda2.sub %>% mutate(MONTH = substr(mmdd, 1, 2))
nelda2.sub <- nelda2.sub %>% mutate(country_id_year_month =  paste(country_id_year, MONTH, sep = "_"))

nelda2.sub <- nelda2.sub %>% left_join(diem_sub, by = c("country_id_year_month")) ## Gotta figure out a way to merge by election--including month

@@

## Adding in Mass Mob events

```{r}
massmob <- read.csv(here::here("Data", "mmALL_073119_csv.csv"))

massmob <- massmob %>% mutate(country_id = countrycode(sourcevar = ccode, origin = "p4n", 
                                               destination = "vdem")) #Missing here tend to be communist
massmob <- massmob %>% mutate(country_id_year = paste(country_id, year, sep = "_"))

#nelda <- nelda %>% mutate(mmdd = ifelse(mmdd < 1000, paste0(0, mmdd), mmdd))

#nelda <- nelda %>% mutate(election_mdy = paste0(mmdd, year))
#nelda <- nelda %>% mutate(election_mdy = mdy(election_mdy))

massmob <- massmob %>% mutate(startday = ifelse(startday < 10, paste0(0, startday), startday))
massmob <- massmob %>% mutate(startmonth = ifelse(startmonth < 10, paste0(0, startmonth), startmonth))

massmob <- massmob %>% mutate(endday = ifelse(endday < 10, paste0(0, endday), endday))
massmob <- massmob %>% mutate(endmonth = ifelse(endmonth < 10, paste0(0, endmonth), endmonth))

massmob <- massmob %>% mutate(protest_mdy = ifelse(is.na(startday) == T | is.na(startmonth) == T, NA,  paste0(startmonth, startday, year)))
massmob <- massmob %>% mutate(protest_mdy_end = ifelse(is.na(endday) == T | is.na(endmonth) == T, NA,  paste0(endmonth, endday, year)))

massmob <- massmob %>% mutate(protest_mdy = mdy(protest_mdy))
massmob <- massmob %>% mutate(protest_mdy_end = mdy(protest_mdy_end))

massmob <- massmob %>% filter(is.na(protest_mdy) == F)

massmob <- massmob %>% filter(is.na(country_id) == FALSE)

## Getting the mass mob events

nelda_selection <- nelda2.sub %>% dplyr::select(NeldaID, country_id.x, election_mdy)

  election_id_temp <- nelda_selection$NeldaID[1]
  country_temp <- nelda_selection$country_id[1]
  election_date_temp <- nelda_selection$election_mdy[1] # Get the election date
  election_row <- nelda_selection[1,]  # Get the election at hand (all Nelda data)
  massmob_temp <- massmob %>% filter(country_id == country_temp) #Get all protests from the country at hand
  massmob_temp <- massmob_temp %>% mutate(days_to_election = election_date_temp - protest_mdy) # Get the days between each protest and the election
  massmob_temp <- massmob_temp %>% filter(days_to_election <= 180 & days_to_election >= -180) #Remove elections outside the window--upped to 180 days
  massmob_temp <- massmob_temp %>% mutate(NeldaID = election_id_temp)
  election_row <- election_row %>% left_join(massmob_temp, by = "NeldaID") #Merge Nelda data with remaining protests

nelda_massmob <- election_row #Start the dataset

for (i in 2:nrow(nelda2.sub)) {  #
  election_id_temp <- nelda_selection$NeldaID[i]
  country_temp <- nelda_selection$country_id[i]
  election_date_temp <- nelda_selection$election_mdy[i]
  election_row <- nelda_selection[i,]
  massmob_temp <- massmob %>% filter(country_id == country_temp)
  massmob_temp <- massmob_temp %>% mutate(days_to_election = election_date_temp - protest_mdy)
  massmob_temp <- massmob_temp %>% filter(days_to_election <= 180 & days_to_election >= -180)

  massmob_temp <- massmob_temp %>% mutate(NeldaID = election_id_temp)
  election_row <- election_row %>% left_join(massmob_temp, by = "NeldaID")
  nelda_massmob <- bind_rows(nelda_massmob, election_row)

## Remove non-election related protests
nelda_massmob <- nelda_massmob %>% rename(notes_massmob = notes)

nelda_massmob <- nelda_massmob %>% filter(is.na(protest_mdy) == T | protest_mdy < election_mdy | (protest_mdy >= election_mdy & str_detect(notes_massmob, regex(pattern = "elector*|election*|vot*|ballot*", ignore_case = T)))) #Turn this on to focus only on protests related to the election

##Next get number and duration
nelda_massmob <- nelda_massmob %>% mutate(protest_mdy_end = ifelse(is.na(protest_mdy_end) == T, protest_mdy, protest_mdy_end)) #This codes protests with no end date as lasting ending on same day they began

nelda_massmob <- nelda_massmob %>% mutate(protest_days = as.Date(protest_mdy_end) - as.Date(protest_mdy))
nelda_massmob <- nelda_massmob %>% mutate(protest_days = ifelse(is.na(protest_mdy)==F & is.na(protest_mdy_end)==T, 1, protest_days))

nelda_massmob.pre <- nelda_massmob %>% filter(as.numeric(days_to_election) > 0) #protest_mdy < election_mdy
nelda_massmob.post <- nelda_massmob %>% filter(as.numeric(days_to_election) <= 0)

## Count
count_data_mm_pre <- nelda_massmob.pre %>% group_by(NeldaID) %>% summarize(n.events.massmob.pre = n())
count_data_mm_post <-nelda_massmob.post %>% group_by(NeldaID) %>% summarize(n.events.massmob.post = n())

## Total duration

dur_data_mm_pre <- nelda_massmob.pre %>% group_by(NeldaID) %>% summarize(mm_duration.pre = as.Date(max(protest_mdy_end, na.rm = T)) - as.Date(min(protest_mdy, na.rm=T)))
dur_data_mm_post <-nelda_massmob.post %>% group_by(NeldaID) %>% summarize(mm_duration.post = as.Date(max(protest_mdy_end, na.rm = T)) - as.Date(min(protest_mdy, na.rm=T)))

## Merge back into nelda

##Combined post data together, then pre data, then both
mm_data_post_comb <- left_join(count_data_mm_post, dur_data_mm_post, by = "NeldaID")
mm_data_pre_comb <- left_join(count_data_mm_pre, dur_data_mm_pre, by = "NeldaID")

mm_data_comb <- left_join(mm_data_pre_comb, mm_data_post_comb, by = "NeldaID")

#mm_data_comb <- mm_data_comb %>% rename(electionid = NeldaID)

## Merge back to Nelda classic
nelda2.sub <- nelda2.sub %>% left_join(mm_data_comb, by = "NeldaID")

#nelda_massmob <- nelda_massmob %>% left_join(mm_data_comb, by = "electionid")  ## Double check to make sure this joining works

## Code NAs for number of protests as 0s (these reflect election years recorded in NELDA where there were no protests recorded by MM)

nelda2.sub <- nelda2.sub %>% mutate(n.events.massmob.pre = ifelse(is.na(n.events.massmob.pre)==T, 0, n.events.massmob.pre))
nelda2.sub <- nelda2.sub %>% mutate(n.events.massmob.post = ifelse(is.na(n.events.massmob.post)==T, 0, n.events.massmob.post))

nelda2.sub <- nelda2.sub %>% mutate(mm_duration.pre = ifelse(is.na(mm_duration.pre)==T, 0, mm_duration.pre))
nelda2.sub <- nelda2.sub %>% mutate(mm_duration.post = ifelse(is.na(mm_duration.post)==T, 0, mm_duration.post))

```{r}
write.csv(nelda2.sub, here::here("Data", "nelda2_sub_2024-02-06.csv"))
```
